Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-05-27 double_blind/reviews.tex
[major] add comments from sensei

		                   & Angle of inclination is defined in 2D and not as a 3D angle, is it sufficient?                                                                                                                                                                                                                                                                                                                                             & \textit{More description added.}                                                                                                            \\ \cline{2-3}

@@

		                   & Modified DMP has not been discussed anywhere in the paper except in figure 3.                                                                                                                                                                                                                                                                                                                                              & \textit{More description added.}                                                                                                            \\ \cline{2-3}

@@

		\multirow{3}{*}{3} & End-effector forces may be shown through a diagram or through some description.                                                                                                                                                                                                                                                                                                                                            & \textit{Description added.}                                                                                                                 \\ \cline{2-3}

>>>>

		                   & Angle of inclination is defined in 2D and not as a 3D angle, is it sufficient?                                                                                                                                                                                                                                                                                                                                             & \textit{Agree that 2D angle is not sufficient. However in this study we considered the adaptability to 2D. Caption of the figure was modified accordingly.}                                                                                                            \\ \cline{2-3}

@@

		                   & Modified DMP has not been discussed anywhere in the paper except in figure 3.                                                                                                                                                                                                                                                                                                                                              & \textit{It seems that the reviewer was getting confused with ``Modified'' keyword. Hence a new keyword ``Initial DMP'' is introduced. Now, the paper contains ``Initial DMP'' and ``Modified DMP''. This has been updated in the paper.}                                                                                                            \\ \cline{2-3}

@@

		\multirow{3}{*}{3} & End-effector forces may be shown through a diagram or through some description.                                                                                                                                                                                                                                                                                                                                            & \textit{Caption of the figure was modified accordingly.}                                                                                                                 \\ \cline{2-3}

### 2017-05-27 paper/paper.tex
[major] add comments from sensei

\author{Ravi P. Joshi}
\authornote{Ravi P. Joshi is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
\affiliation{}
\email{joshi-ravi-prakash@edu.brain.kyutech.ac.jp}

\author{Nishanth Koganti}
\authornote{Nishanth Koganti is with Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan and Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
\affiliation{}
\email{nishanth-k@is.naist.jp}

\author{Tomohiro Shibata}
\authornote{Tomohiro Shibata is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Fukuoka, Japan}
\affiliation{}
\email{tom@brain.kyutech.ac.jp}

@@

Trajectory variability for clothing assistance is large for different environmental conditions. We need to parametrize the task efficiently so that generalization can be acheived quickly. In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance task. Robotic cloth manipulation task deals with putting a clothing article on both the arms. The idea of using DMP is inspired by the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design a controller from scratch or to fine-tune various controller parameters. We choose dual arm Baxter robot in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.

>>>>

\author{Ravi P. Joshi}
\authornote{Ravi P. Joshi is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan}
\affiliation{}
\email{joshi-ravi-prakash@edu.brain.kyutech.ac.jp}

\author{Nishanth Koganti}
\authornote{Nishanth Koganti is with Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan and Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan}
\affiliation{}
\email{nishanth-k@is.naist.jp}

\author{Tomohiro Shibata}
\authornote{Tomohiro Shibata is with Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan}
\affiliation{}
\email{tom@brain.kyutech.ac.jp}

@@

Trajectory variability for clothing assistance is large for different environmental conditions. We need to parametrize the task efficiently so that generalization can be acheived quickly. In this study, we are investigating the applicability of using Dynamic Movement Primitives (DMP) as a task parameterization model for performing clothing assistance task. Robotic cloth manipulation task deals with putting a clothing article on both the arms. The idea of using DMP is inspired by the fact that DMP can learn complex task from the demonstration \cite{ijspeert2003learning, schaal2006dynamic, ijspeert2013dynamical} and thus reduce the manual efforts to design a controller from scratch or to fine-tune various controller parameters. We choose dual arm Baxter robot (Rethink robotics) in this research as it is safe and flexible by design \cite{fitzgerald2013developing}.
